Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-26 pre_post_biorxiv.tex
Fix italics

% title goes here:
\begin{flushleft}
{\LARGE
\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour}
}
\newline
% authors go here:
\\
A. Bradley Duthie\textsuperscript{1,*},
Jane M. Reid\textsuperscript{1},
\\
\bigskip
\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
%\\
%\bf{2} Affiliation B
\\
\bigskip
*  aduthie@abdn.ac.uk, brad.duthie@gmail.com

@@

Here we use individual-based modelling and *in silico* experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry. Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations. Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive. We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.

>>>>

% title goes here:
\begin{flushleft}
{\LARGE
\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour}
}
\newline
% authors go here:
\\
A. Bradley Duthie\textsuperscript{1,*},
Jane M. Reid\textsuperscript{1}
\\
\bigskip
\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
%\\
%\bf{2} Affiliation B
\\
\bigskip
*  aduthie@abdn.ac.uk, brad.duthie@gmail.com

@@

Here we use individual-based modelling and \textit{in silico} experiments to test the hypothesis that, given severe inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance causes selection for polyandry. Additionally, we test the hypothesis that costs associated with polyandry and inbreeding strategies will strongly affect evolution of each such that selection for only the less costly inbreeding avoidance strategy will be sustained over generations. Finally, we test the hypothesis that evolution of one inbreeding strategy will be precluded if it is introduced into a population that is already fixed for a complementary inbreeding strategy that is adaptive. We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and strong inbreeding depression in offspring viability.
